---
title: "R Notebook"
output: html_notebook
---

Problem 1:
All the cleaning and organizing of the data is done here:

```{r}
library(dplyr)
library(stringr)
library(lubridate)
library(ggplot2)

orders = read.csv('./data/Orders.csv')

money = function(x){
  x = str_remove_all(x, fixed('$'))
  x = str_remove_all(x, ',')
  return(as.numeric(x))
}


orders = orders %>% mutate(Profit = money(Profit), Sales = money(Sales))

orders = orders %>% mutate(Order.Date = mdy(Order.Date))

orders = orders %>% mutate(Month = month(Order.Date), Year = year(Order.Date), Quarter = quarter(Order.Date))

head(orders)
```


```{r}
orders %>% group_by(Quarter) %>% summarize(Total_Orders = sum(Quantity))
orders %>% group_by(Category,Quarter) %>% summarize(Total_Orders = sum(Quantity)) %>% ggplot(., aes(x = Quarter, y = Total_Orders)) + geom_col(aes(color = Category), position = position_dodge())
```
Problem 2:
As shown above there are clearly more Total_Orders in Q4 and less in Q1.And it does follow for all of the categories

Problem 3:
	1. How much profit did we lose due to returns each year?
	Taking this to mean any negative profit:
```{r}
orders %>% filter(Profit < 0) %>% summarize(lost_profit = sum(Profit))
```
	


	2. How many customer returned more than once? more than 5 times?
```{r}
orders %>% filter(Profit < 0) %>% group_by(Customer.ID) %>% count() %>% filter(n>4) %>% nrow()
```
	


	3. Which regions are more likely to return orders?
```{r}
orders %>% filter(Profit < 0) %>% group_by(Region) %>% count() %>% 
  arrange(desc(n)) %>% ggplot(., aes(x = reorder(Region,-n), y = n)) + geom_col() + theme(axis.text.x = element_text(face="bold",  angle=90))
```
	


	4. Which categories (sub-categories) of products are more likely to be returned?

```{r}
orders %>% filter(Profit < 0) %>% group_by(Category,Sub.Category) %>% count() %>% ggplot(., aes(x = reorder(Sub.Category,-n), y = n)) + geom_col() + theme(axis.text.x = element_text(face="bold",  angle=90))
```


```





Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

